Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-24 methods_paper/fabl-paper.tex
update.
working on fs.

\bigskip
\begin{abstract}
In this paper, we propose the \emph{fast beta linkage} (\texttt{fabl}), which extends a recent Bayesian Fellegi Sunter model to allow for parallel computing. In addition, we propose using hashing techniques to hasten calculations and to reduce the overall computational complexity. To achieve a scalable model, we propose independent priors in order to create computational speeds and gains, where we relax the one-to-one matching assumption. Second, we resolve the one-to-one matching issue via a post processing step. Third, we derive conditional distributions, a Gibbs sampler, and corresponding Bayes estimates for our proposed model. Fourth, we explore other computational speeds up based upon storage efficient indexing. Finally, we explore a sensitivity analysis and revisit the case study of the El Salvadoran conflict to understand the practical ramifications regarding our proposed modeling choices, where we provide comparisons to the \text{BRL} package in CRAN. 
\end{abstract}

\noindent%
{\it Keywords:} record linkage, bipartite record linkage, Bayesian methods, Gibbs sampling, hashing techniques, Markov chain Monte carlo

@@

>>>>

\bigskip
\begin{abstract}
In this paper, we propose the \emph{fast beta linkage} (\texttt{fabl}) methods, which extends a recent Bayesian Fellegi Sunter model to allow for parallel computing. In addition, we propose using hashing techniques to hasten calculations and to reduce the overall computational complexity. To achieve a scalable model, we propose independent priors in order to create computational speeds and gains, where we relax the one-to-one matching assumption. Second, we resolve the one-to-one matching issue via a post processing step. Third, we derive conditional distributions, a Gibbs sampler, and corresponding Bayes estimates for our proposed model. Fourth, we explore other computational speeds up based upon storage efficient indexing. Finally, we explore a sensitivity analysis and revisit the case study of the El Salvadoran conflict to understand the practical ramifications regarding our proposed modeling choices, where we provide comparisons to the \text{BRL} package in CRAN. 
\end{abstract}

\noindent%
{\it Keywords:} record linkage, bipartite record linkage, Bayesian methods, Gibbs sampling, hashing techniques, Markov chain Monte carlo, parallel/distributed computing

@@

\subsection{Comparison Data}
